Type Checker Generation using Reference Attribute Grammars

### 2023-10-16 MSc.tex
Add architectural overview graph

\documentclass[nofilelist]{cslthse-msc}
% to show a list of used packages at the end of the document, delete the nofilelist option
%\documentclass{cslthse-msc}
\usepackage[utf8]{inputenc}
\usepackage[british]{babel}
\usepackage{amsmath}
%\usepackage{amsfonts}
%%\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{makeidx}
\usepackage{graphicx}
\usepackage[titletoc, header, page]{appendix}
\usepackage{transparent}

@@

\section{Architecture}
Overview
\subsection{Typing rule definition}
Custom DSL
ASCII representation of natural deduction %BNF (is it BNF?)
\subsubsection{Language}
Figure of example natural deduction rules (from Pierce?) and ASCII representation
\subsubsection{Parser}
\subsubsection{Abstract syntax tree}

>>>>

\documentclass[nofilelist]{cslthse-msc}
% to show a list of used packages at the end of the document, delete the nofilelist option
%\documentclass{cslthse-msc}
\usepackage[utf8]{inputenc}
\usepackage[british]{babel}
\usepackage{amsmath}
%\usepackage{amsfonts}
%%\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{makeidx}
\usepackage{graphicx}
\usepackage[titletoc, header, page]{appendix}
\usepackage{transparent}
\usepackage{tikz}
\usetikzlibrary{fit,positioning,shapes.geometric}

@@

\section{Architecture}
Overview

\noindent\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
  every node/.style = {draw=black, rounded corners, align=center},
  every path/.style = {draw, -latex}
                          ]
  \node (typerules)                               {Object language typing\\ rules definition};
  \node (trparsing) [right=of typerules, ellipse] {scan,\\parse,\\build};
  \node (trparser)  [above=of trparsing]          {Typing rule parser};
  \node (trast)     [right=of trparsing]          {Typing rules AST};

  \node (typecheckgen) [below=of trast, ellipse] {
    \textbf{Type checker generation}\\
    - Link rules and language AST\\
    - Fill in template
  };

  \node (olast)     [below=of typerules] {Object language AST};
  \node (inputprog) [below=of olast]     {Input program};

  \node (outputparsing)      [below=of typecheckgen, ellipse]  {Scan,\\parse,\\build};
  \node (outputtypechecking) [right=of outputparsing, ellipse] {Perform\\typechecking};
  \node (typeerrors)         [right=of outputtypechecking]     {List of type errors};

  \node (template) [right=of typecheckgen] {
    \textbf{Type checker template}\\
    - Scanner, parser, builder\\
    - Project files\\
    - Type checking algorithm\\
  };

  \node (userinput)   [dashed, fill=none, fit=(typerules) (olast)]                  {};
  \node               [above, draw=none] at (userinput.north)                       {User input};
  \node (typechecker) [dashed, fill=none, fit=(outputparsing) (outputtypechecking)] {};
  \node               [above, draw=none] at (typechecker.north)                     {Type checker};

  \draw   (typerules)  to  (trparsing);
  \draw   (trparser)  to  (trparsing);
  \draw   (trparsing)  to  (trast);
  \draw   (trast)  to  (typecheckgen);
  \draw   (olast)  to  (typecheckgen);
  \draw   (olast)  to  (outputparsing);
  \draw   (outputparsing)  to  (outputtypechecking);
  \draw   (outputtypechecking)  to  (typeerrors);
  \draw   (typecheckgen)  to  (typechecker);
  \draw   (inputprog)  to  (outputparsing);
  \draw   (template)  to  (typecheckgen);

\end{tikzpicture}
}

\subsection{Typing rule definition}
Custom DSL
ASCII representation of natural deduction %BNF (is it BNF?)
\subsubsection{Language}
Figure of example natural deduction rules (from Pierce?) and ASCII representation
\subsubsection{Parser}
\subsubsection{Abstract syntax tree}
